Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-11-21 SEIR.tex
fix typo

The parameters $\beta_t$ absorb all the time-varying factors not captured by Google mobility and school attendance data.
\todo{discuss the results and implications for policy or understanding transmission}
Many factors contribute to the pattern in the $\beta_t$ values, which have a minima near the start of December.
While this analysis cannot establish causation, several hypotheses can be identified that are worth further investigation.
The decreases in $\beta_t$ over the autumn could be due to increased caution as cases and deaths increased (\eg masking or stricter adherence to social distancing)\todo{cite something about caution and reaction to rising cases, or survey data showing this happened - CoMix?}, or the impact of local measures in the highest transmission areas\todo{cite local measures}.
The increases in $\beta_t$ in December coincide with the rise of the Alpha variant~\autoref{lythgoeLineage}, known to be more transmissible~\auocite{daviesEstimated}.
A multiple variant model might be able to capture this rise more accurately.
Such a model would stratify positive tests in the CIS by pre-Alpha or Alpha variant.
Then, each variant would be explicitly included in the model to fit to this data.

>>>>

The parameters $\beta_t$ absorb all the time-varying factors not captured by Google mobility and school attendance data.
\todo{discuss the results and implications for policy or understanding transmission}
Many factors contribute to the pattern in the $\beta_t$ values, which have a minima near the start of December.
While this analysis cannot establish causation, several hypotheses can be identified that are worth further investigation.
The decreases in $\beta_t$ over the autumn could be due to increased caution as cases and deaths increased (\eg masking or stricter adherence to social distancing)\todo{cite something about caution and reaction to rising cases, or survey data showing this happened - CoMix?}, or the impact of local measures in the highest transmission areas\todo{cite local measures}.
The increases in $\beta_t$ in December coincide with the rise of the Alpha variant~\autoref{lythgoeLineage}, known to be more transmissible~\autocite{daviesEstimated}.
A multiple variant model might be able to capture this rise more accurately.
Such a model would stratify positive tests in the CIS by pre-Alpha or Alpha variant.
Then, each variant would be explicitly included in the model to fit to this data.
